Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-27 mr-review.Rmd
added new section on overlapping samples

@fang2021evaluating

@sadreev2021navigating

@@

>>>>

@@

## Sample overlap

The issue of overlapping samples in the two-sample MR with GWAS summary data has recently 
received attention in the published literature.

@fang2021evaluating, working with data from the UK Biobank, found that SNP instruments 
derived from overlapping samples explained a higher proportion of the variance compared to 
those derived from non-overlapping samples. They surmise that block jackknife resampling MR
enables causal inference while avoiding bias due to overlapping samples.

@sadreev2021navigating analyzed 2,514 traits from the UK Biobank and evaluated the impact of winner's curse on MR analysis. Winner's curse, they found, amplifies weak instrument bias without 
inflating the false discovery rate. This finding led the authors to design a pseudoreplication process that reduces bias in MR studies.
